---
title: "Appendix B: Exploratory analyses"
bibliography: ../bibliography/bibliography-marginal.bib
csl: ../bibliography/apa.csl
output: word_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, echo=FALSE, warning=FALSE, message=FALSE)
```
```{r r_objects}
marginal <- readRDS("./marginal_rmarkdown_objects.RData")
```

##Appendix B: Exploratory analyses
Our estimates of the incidence of 'marginal significance' in JPSP and DP differ from those of @10.1177/0956797616645672, for which there may be several contributing reasons. We estimated the percentage of 'marginally significant' results in JPSP as `r marginal$marg.jpsp`% vs. @10.1177/0956797616645672's `r marginal$pritschet.jpsp`%, and for DP as `r marginal$marg.dp`% vs. `r marginal$pritschet.dp`%. Two things that might contribute to these differences are: 1) @10.1177/0956797616645672 only observing a few select years and 2) the difference in DVs. We explore these possibilites below.

It may be that @10.1177/0956797616645672 coincidentally only examined years with lower percentages of 'marginally significant' results. Of the five years examined by @10.1177/0956797616645672 our data includes three (1990/2000/2010). Using only these three years we estimated the percent 'marginally significant' _p_-values in JPSP and DP. However, this leads to an estimate for our DV that is slightly higher than before, both for JPSP (`r marginal$marg.p.jpsp.1990.2010`%) and DP (`r marginal$marg.p.dp.1990.2010`%). The difference in years examined is thus not a good explanation for the difference in estimates between @10.1177/0956797616645672 and us.

Differences may partly be due to differences in dependent variables. Equation 1 indicates how we calculated the incidence of 'marginally significant' results, and equation 2 how @10.1177/0956797616645672 calculated it. Comparing the results of our DV and the DV of @10.1177/0956797616645672 for the same years and data permits us to explore how the difference in DVs can affect estimates. Doing this for the years 1990/2000/2010 in our data, our DV still yields higher estimates of the percentage 'marginally significant' results for both JPSP (by `r marginal$marg.p.jpsp.1990.2010 - marginal$marg.a.jpsp.1990.2010`%) and DP (by `r marginal$marg.p.dp.1990.2010 - marginal$marg.a.dp.1990.2010`%). However, these values are close to the actual differences in estimates between @10.1177/0956797616645672 and us for JPSP (`r marginal$marg.jpsp - marginal$pritschet.jpsp`%) and DP (`r marginal$marg.dp - marginal$pritschet.dp`%). Differences in estimates between @10.1177/0956797616645672 and us thus largely result from the difference in dependent variables. The remaining small differences may be due to minor differences in data, e.g. @10.1177/0956797616645672 report low proportions of 'marginally significant' results for the years not included in our sample (1970/1980) and include _p_-values  > .1 in their count of 'marginally significant' results.

$$\text{Incidence marg. sig. results} = \frac{\text{Marg. sig. p-values }(.05<p\leq.1)}{\text{All p-values }(.05<p\leq.1)}\text{ (1)}$$

$$\text{Incidence marg. sig. results} = \frac{\text{Articles with }\geq1\text{ marg. sig. p-value}}{\text{All articles with p-values}}\text{ (2)}$$ 

###References