---
title: "Appendix B: Possible reasons for the differences in estimates between Pritschet et al. (2016)'s and ours"
bibliography: ../bibliography/bibliography-marginal.bib
csl: ../bibliography/apa.csl
output: word_document
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, echo=FALSE, warning=FALSE, message=FALSE)
```
```{r r_objects}
marginal <- readRDS("./marginal_rmarkdown_objects.RData")
```

##Appendix B: Exploratory analyses
Our estimates of the incidence of 'marginal significance' in JPSP and DP differ from those of @10.1177/0956797616645672, for which there may be several contributing reasons. We estimated the percentage of 'marginally significant' results in JPSP as `r marginal$marg.jpsp`% vs. @10.1177/0956797616645672's `r marginal$pritschet.jpsp`%, and for DP as `r marginal$marg.dp`% vs. `r marginal$pritschet.dp`%. Two things that might contribute to these differences are: 1) @10.1177/0956797616645672 only observe a few select years and 2) the difference in DVs. We explore these possibilites below.

It may be that @10.1177/0956797616645672 coincidentally only examined years with lower percentages of 'marginally significant' results (see Figure 2 of our manuscript). Of the five years examined by @10.1177/0956797616645672 we used only the data of years 1990, 2000, 2010). However, using the data of only these years our estimates were slightly higher than before and not lower (`r marginal$marg.p.jpsp.1990.2010`% for JPSP and `r marginal$marg.p.dp.1990.2010`% for DP). Consequently, the difference in years examined does not explain the difference in @10.1177/0956797616645672's estimates and ours.

Differences in estimates are mainly due to differences in the dependent variables of both studies. The estimator used by @10.1177/0956797616645672 divides the number of articles reporting 'marginally significant' results by the total number of articles containing _p_-values. Hence the denominator not only includes the number of articles with _p_-values between .05 and .1, but also the number of articles without these _p_-values. The number of articles without these _p_-values is substantial; in our dataset `r marginal$total.a.without.p.outside.range` out of `r marginal$articles.with.p` articles did not contain them. Hence including the number of articles without these _p_-values in the denominator decreases estimates substantially, thereby explaining why @10.1177/0956797616645672's estimates are considerably smaller than ours. Another difference between the two estimators is that ours is at the level of individual results and @10.1177/0956797616645672's is at the level of articles. In theory, this difference may result in very different estimates, with generally higher values for @10.1177/0956797616645672's estimate than ours as the number of _p_-values between .05 and .1 per article increases. However, as the number of _p_-values between .05 and .1 per article is low (around 1, see Table 1 of our manuscript), the difference in level of analysis will not greatly contribute to the difference between ours and @10.1177/0956797616645672's estimates of the incidence of 'marginal significance' in JPSP and DP.

###References